---
title: 'Stats for the 2019/2020 hockey season'
author: Kjartan Kloster Osmundsen
date: '2020-03-15'
slug: updated-hockey-stats
categories:
  - Web scraping
  - Hockey
  - R
tags: []
image:
  caption: ''
  focal_point: ''
---

This post is simply my previous hockey scripts applied to data for the 2019/2020 season, both the [Stavanger Oilers player statistics](https://www.kjartako.no/post/web-scraping-with-r-visualizing-hockey-statistics/) and [aggregated statistics for the Norwegian league](https://www.kjartako.no/post/hockey-web-scraping-data-aggregation/). 

However, after recently reading the book [Storytelling with data](http://www.storytellingwithdata.com/books), I felt obligated to make some minor changes to the graphs from last season. 

# Stavanger Oilers player statistics

```{r f,include=FALSE}
library(rvest)
library(ggplot2)

########
special_chars = list('S'='S', 's'='s', 'Z'='Z', 'z'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Ç'='C', 'È'='E', 'É'='E',
                          'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ù'='U',
                          'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'ç'='c',
                          'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                          'ö'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )
########
#system("./phantomjs season_scrape.js")
season_dat = read_html("data/season20.html",encoding ="UTF-8")
season=season_dat%>%html_nodes("table")%>%.[[1]]%>%html_table()

for(i in 1:nrow(season))
{
  tmp=strsplit(season$PLAYER[i], ",")[[1]]
  season$PLAYER[i]=paste(substr(tmp[2],2,2),tmp[1])
}
##########
EP = read_html("https://www.eliteprospects.com/team/845/stavanger-oilers/2019-2020?tab=stats")
EPdat=EP%>%html_nodes("table")%>%.[[2]]%>%html_table()
EPstats = EPdat[!is.na(EPdat[,1]),]

names=setNames(data.frame(matrix(ncol = 3, nrow = nrow(EPstats))), c("NAME", "POSITION", "PLAYER"))

for(j in 1:nrow(EPstats))
{
  tmp=strsplit(EPstats$Player[j], "\\s+")[[1]]
  names$NAME[j]=paste((tmp[-length(tmp)]),collapse = " ")
  names$POSITION[j]=tmp[length(tmp)]
  # Replaces accented characters
  firstname1 = substr(chartr(paste(names(special_chars), collapse=''),paste(special_chars, collapse=''),tmp[1]),1,1)
  lastname = chartr(paste(names(special_chars), collapse=''),paste(special_chars, collapse=''),tmp[length(tmp)-1])
  names$PLAYER[j]= paste(firstname1,lastname)
}

season = merge(season,names)
```

```{r fig1, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}

season$col <- cut(
  season$PTS/season$GP, 
  breaks=c(0, 0.25, 0.5, 0.75, 1, Inf)
)

ggplot(season[season$PTS>0,],aes(x=PTS/GP,y=reorder(NAME,PTS/GP),fill=col))+
  geom_segment(aes(yend=NAME,x=G/GP,xend=0),colour="black",size=1.5)+
  geom_segment(aes(yend=NAME,x=PTS/GP,xend=G/GP),colour="grey50",size=1)+
  geom_point(size=4,shape=21)+theme_bw()+ylab("")+xlab("Total points per game (goals in black)")+
  scale_x_continuous(position = "top",expand = c(0, 0),breaks = seq(from=0,by=0.25,to=max(season$PTS/season$GP)),limits = c(0,max(season$PTS/season$GP)*1.1))+
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")+scale_fill_brewer("", palette = "Blues")+
  theme(axis.text=element_text(size=14),axis.title=element_text(size=14,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))

```

<br/>
<br/>

```{r fig2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}

season$col <- cut(
  season$GWG,
  breaks=c(2, 3, 4, 5, Inf)
)

ggplot(season[season$GWG>0,],aes(x=GWG,y=reorder(NAME,GWG),fill=col))+
  geom_segment(aes(yend=NAME,x=0,xend=GWG),colour="grey50",size=1)+
  geom_point(size=4,shape=21)+theme_bw()+ylab("")+xlab("GWG")+
  scale_x_continuous(position = "top",expand = c(0, 0),limits = c(0,max(season$GWG)*1.1))+
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")+scale_fill_brewer("", palette = "Blues")+
  theme(axis.text=element_text(size=14),axis.title=element_text(size=14,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))

```

<br/>
<br/>

```{r fig3, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}

season$col <- cut(
  season$PPA+season$PP,
  breaks=c(5, 10, 15, 20, 25, Inf)
)

ggplot(season[season$PPA+season$PP>0,],aes(x=PPA+PP,y=reorder(NAME,PPA+PP),fill=col))+
  geom_segment(aes(yend=NAME,x=PP,xend=0),colour="black",size=1.5)+
  geom_segment(aes(yend=NAME,x=PPA+PP,xend=PP),colour="grey50",size=1)+
  geom_point(size=4,shape=21)+theme_bw()+ylab("")+xlab("Total powerplay points (goals in black)")+
  scale_x_continuous(position = "top",expand = c(0, 0),breaks = seq(from=0,by=5,to=max(season$PPA+season$PP)),limits=c(0,max(season$PPA+season$PP)*1.1))+
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")+scale_fill_brewer("", palette = "Blues")+
  theme(axis.text=element_text(size=14),axis.title=element_text(size=14,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))

```

<br/>
<br/>

```{r fig4, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}

season$col <- cut(
  season$PIM,
  breaks=c(15, 50, 75, 100, Inf)
)

ggplot(season[season$PIM>0,],aes(x=PIM,y=reorder(NAME,PIM),fill=col))+
  geom_segment(aes(yend=NAME,x=0,xend=PIM),colour="grey50",size=1)+
  geom_point(size=4,shape=21)+theme_bw()+ylab("")+xlab("Penalty minutes")+
  scale_x_continuous(position = "top",expand = c(0, 0),breaks = seq(from=0,by=20,to=max(season$PIM)),limits = c(0,max(season$PIM)*1.1))+
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")+scale_fill_brewer("", palette = "Blues")+
  theme(axis.text=element_text(size=14),axis.title=element_text(size=14,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))

```

# League statistics


```{r f2,include=FALSE}
library(ggplot2)
library(reshape2)

#antall kamper: 225

MATCHLIST=readRDS(file="data/matches20.rds")
N = length(MATCHLIST)

teams=c("Frisk Asker Elite","Grüner","Lillehammer Elite","Manglerud Star Elite","Narvik","Sparta Elite",
        "Stavanger Ishockeyklubb","Stjernen Elite","Storhamar Elite","Vålerenga Elite")

teams_displaynames=c("Frisk Asker","Grüner","Lillehammer","Manglerud Star","Narvik","Sparta",
                     "Stavanger Oilers","Stjernen","Storhamar","Vålerenga")
n = length(teams)
######################################################################################
######################################################################################
######################################################################################
# GOALS PER PERIOD 
######################################################################################
######################################################################################
######################################################################################

res = data.frame(Team=teams_displaynames,s1=rep(0,n),s2=rep(0,n),s3=rep(0,n),s4=rep(0,n),g1=rep(0,n),g2=rep(0,n),g3=rep(0,n),g4=rep(0,n),Gamecount=rep(0,n),OTcount=rep(0,n))

for(j in 1:length(teams))
{
  Gamecount=0
  OTcount=0
  goals=rep(0,4)
  shots=rep(0,4)
  
  for(i in 1:N)
  {
    if(is.element(teams[j],MATCHLIST[[i]]$scoring[,1]))
    {
      tmp=MATCHLIST[[i]]$scoring
      
      homeaway=which(teams[j] == tmp[,1])
      
      if(ncol(tmp)>13)
      {
        goals=goals+as.numeric(tmp[homeaway,3:6])
        tmpid=which("Shots"==colnames(tmp))
        shots=shots+as.numeric(tmp[homeaway,(tmpid+1:4)])
        
        if(sum(tmp[,6:7])>0)
        {
          OTcount=OTcount+1
        }
        
      }else
      {
        goals=goals+c(as.numeric(tmp[homeaway,3:5]),0)
        shots=shots+c(as.numeric(tmp[homeaway,7:9]),0)
      }
      Gamecount=Gamecount+1
    }
  }
  
  res[j,2:5]=shots
  res[j,6:9]=goals
  res[j,10:11]=c(Gamecount,OTcount)
}

##############################################
eff = round(100*(res[,6:8]/res[,2:4]),1)
colnames(eff)=c("eff1","eff2","eff3")
eff = melt(cbind(Team=res[,1],eff),id.vars = "Team")
eff=cbind(eff,as.vector(as.matrix(t(apply(res[,6:8],1,cumsum))-0.5*res[,6:8])))
colnames(eff)=c("Team","Period","eff","pos")

goaldat = melt(res[,c(1,6:8)],id.vars = "Team")
colnames(goaldat)=c("Team","Period","Goals")

goaldat$Period = factor(goaldat$Period, levels = c("g3","g2","g1"))

######################################################################################
######################################################################################
######################################################################################
# ATTENDANCE
######################################################################################
######################################################################################
######################################################################################
attendance = matrix(rep(NA,N*3),ncol=3)

for(i in 1:N)
{
  tmp = MATCHLIST[[i]]$meta
  attendance[i,1] = tmp[which(tmp[,1]=="Attendance"),2]
  attendance[i,2:3] = MATCHLIST[[i]]$scoring[1:2,1]
}


meanvals=numeric(n)

for(i in 1:n)
{
  meanvals[i]=mean(as.numeric(attendance[which(attendance[,2]==teams[i]),1]))
}

devsum=matrix(rep(NA,n*n),ncol=n)
colnames(devsum)=teams_displaynames
rownames(devsum)=teams_displaynames

for(k in 1:n)
{
  for(j in (1:n)[-k])
  {
    devsum[k,j]=100*((mean(as.numeric(attendance[which(attendance[,2]==teams[j] & attendance[,3]==teams[k]),1]))-meanvals[j])/meanvals[j])
  }  
}

##############################################
library(reshape2,quietly = TRUE) #for melt()
library(RColorBrewer,quietly = TRUE) #for brewer.pal()

plotdat = melt(devsum)
names(plotdat) <- c("Away", "Home","val")

plotdat$col <- cut(
  plotdat$val,
  breaks=c(-Inf,0 ,20, 60, Inf)
)
######################################################################################
######################################################################################
######################################################################################
# PENALTIES
######################################################################################
######################################################################################
######################################################################################
pendata = matrix(c("Team","HomeAway","Period","Time","Duration","Type"),ncol=6)

for(j in 1:length(teams))
{
  Gamecount=0
  
  for(i in 1:N)
  {
    if(is.element(teams[j],MATCHLIST[[i]]$scoring[,1]))
    {
      tmp=MATCHLIST[[i]]$scoring
      homeaway=which(teams[j] == tmp[,1])
      
      plist=list(MATCHLIST[[i]]$pen1,MATCHLIST[[i]]$pen2,MATCHLIST[[i]]$pen3)
      
      for(h in 1:3)
      {
        for(k in 1:nrow(plist[[h]]))
        {
          test=strsplit(plist[[h]][k,], "\r\n")[[1]]
          
          if(gsub("\\s", "", gsub("-", "", test[1])) == gsub("\\s", "", teams[j]))
          {
            test2=strsplit(test[3], ", ")[[1]]
            
            timetmp=as.numeric(gsub(":", "", test2[3]))+(h-1)*2000
            pentime=round((timetmp %/% 100)+((timetmp %% 100)/60),2)
            pendur=test2[2]
            pentype=gsub("[\\(\\)]", "", regmatches(test2[1], gregexpr("\\(.*?\\)", test2[1]))[[1]])
            
            pendata=rbind(pendata,c(teams[j],homeaway,h,pentime,pendur,pentype))
          }
        }
      }
      
      Gamecount=Gamecount+1
    }
  }
  
  print(Gamecount)
}

##############################################
res=data.frame(Team=pendata[-1,1],Homeaway=as.numeric(pendata[-1,2]),Period=as.numeric(pendata[-1,3]),Time=as.numeric(pendata[-1,4]),Duration=pendata[-1,5],Type=pendata[-1,6])
res2min=res[res$Duration=="2 min",]
pentab=as.data.frame(sort(table(res2min$Type),decreasing = TRUE))[1:8,]
colnames(pentab)=c("Type","Count")

###

tmpres=res2min[is.element(res2min$Type,pentab$Type),]
pendat=as.data.frame(table(tmpres$Team,droplevels(tmpres$Type)))
colnames(pendat)=c("Team","Type","Count")

pendat$Type = factor(pendat$Type, levels = rev(unique(pendat$Type)))

####

hometab=as.data.frame(table(res2min$Team,res2min$Homeaway))
colnames(hometab)=c("Team","Homeaway","Count")

hometab$Homeaway = factor(hometab$Homeaway, levels = c(2,1))

######################################################################################
######################################################################################
######################################################################################
# REFEREES
######################################################################################
######################################################################################
######################################################################################
refs = matrix(rep(NA,N*4),ncol=4)

for(i in 1:N)
{
  tmp = MATCHLIST[[i]]$meta
  refs[i,1:2] = tmp[which(tmp[,1]=="Hoveddommer"),2]
  refs[i,3:4] = MATCHLIST[[i]]$scoring[1:2,1]
}

##############################################
tmp = cbind(c(refs[,1],refs[,2]),rbind(refs[,3:4],refs[,3:4]))
reftab=rbind(tmp[,1:2],tmp[,c(1,3)])

toprefs=droplevels(as.data.frame(sort(table(reftab[,1]),decreasing = TRUE))[1:15,1])

topreftab=reftab[is.element(reftab[,1],toprefs),]

refcount= as.data.frame(table(topreftab[,1],topreftab[,2])) 
colnames(refcount)=c("Referee","Team","Count")

refcount$Team = factor(refcount$Team, levels = rev(teams))

######################################################################################
######################################################################################
######################################################################################
# TIME ON ICE
######################################################################################
######################################################################################
######################################################################################
TOIdata = data.frame(Team=teams_displaynames,G1=rep(0,n),G2=rep(0,n),G3=rep(0,n),G4=rep(0,n),Games=rep(0,n))

for(j in 1:n)
{
  for(i in 1:N)
  {
    if(is.element(teams[j],MATCHLIST[[i]]$scoring[,1]))
    {
      homeaway=which(teams[j] == MATCHLIST[[i]]$scoring[,1])
      if(homeaway == 1)
      {
        tmp = MATCHLIST[[i]]$home
      }else{
        tmp = MATCHLIST[[i]]$away
      }
      
      TOIs=as.numeric(gsub(":", "", tmp[tmp[,10]!="",10]))
      TOIs=sort(round((TOIs %/% 100)+((TOIs %% 100)/60),2),decreasing = TRUE)
      nt=length(TOIs)
      
      if(nt > 10)
      {
        TOIdata$Games[j] = TOIdata$Games[j] + 1
        TOIdata$G1[j] = TOIdata$G1[j] + mean(TOIs[1:5])
        TOIdata$G2[j] = TOIdata$G2[j] + mean(TOIs[6:10])
        TOIdata$G3[j] = TOIdata$G3[j] + ifelse(nt>14,mean(TOIs[11:15]),mean(TOIs[11:nt]))
        if(nt > 15)
        {
          TOIdata$G4[j] = TOIdata$G4[j] + ifelse(nt<20,mean(TOIs[16:nt]),mean(TOIs[16:20]))  
        }
      }
    }
  }
}
TOIdata=cbind(Team=TOIdata[,1],TOIdata[,2:5]/TOIdata$Games)

#####################################################################

library(reshape2)
TOItop = melt(TOIdata)
colnames(TOItop)=c("Team","Type","Val")
TOItop$Maxval = rep(TOItop$Val[1:n],4)

TOItop$Type = factor(TOItop$Type, levels = c("G4","G3","G2","G1"))

```


```{r fig1-2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}
ggplot() + geom_bar(aes(y = Goals, x = reorder(Team, Goals), fill = Period),colour="black",width=.8,alpha=.8, data = goaldat,stat="identity")+
  coord_flip()+scale_y_continuous(position = "right")+theme_bw()+scale_fill_brewer(palette="Paired",breaks=c("g1", "g2", "g3"),labels=c("First Period", "Second Period", "Third Period"))+
  theme(panel.grid.minor.y=element_blank(),panel.grid.major.y=element_blank())+
  theme(legend.position="top",legend.title=element_blank(),legend.spacing.x = unit(1, 'cm'),legend.text=element_text(size=12),axis.title.y = element_blank())+ylab("Goals scored (shooting percentages)")+
  theme(axis.text.x=element_text(size=18),axis.text.y=element_text(size=14),axis.title=element_text(size=16,face="bold"))+
  geom_text(data=eff, aes(x = Team, y = pos,label = paste0(eff,"%")), size=5)+
  guides(fill = guide_legend(nrow = 1,keywidth=1,keyheight=1,default.unit="cm"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))
```

<br/>
<br/>

```{r fig2-2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 8}
ggplot(plotdat, aes(Away,Home,z=val))+geom_tile(aes(fill=col))+theme_bw()+
  scale_fill_brewer("", palette = "YlGn",na.value="grey",labels=c("Below average","0-20 % increase","20-60 % increase",">60 % increase","NA"))+
  theme(axis.text.x = element_text(angle=60,hjust=1,vjust=1.0))+
  xlab("Away team") + ylab("Home team")+
  theme(legend.text =element_text(size=12),legend.title =element_text(size=14))+
  theme(axis.text.x=element_text(size=14),axis.text.y=element_text(size=14),axis.title=element_text(size=16,face="bold"))+
  theme(legend.position = "top")+guides(fill = guide_legend(nrow = 1,keywidth=0.8,keyheight=0.8,default.unit="cm"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))
```

<br/>
<br/>

```{r fig3-2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}
ggplot() + geom_bar(aes(y = Count, x = reorder(Type,Count)),colour="black",width=.8,alpha=.8, data = pentab,stat="identity")+
  coord_flip()+scale_y_continuous(position = "right")+theme_bw()+theme(panel.grid.minor.y=element_blank(),panel.grid.major.y=element_blank())+
  theme(axis.title.y = element_blank())+ylab("Number of 2 min penalties")+
  theme(axis.text.x=element_text(size=18),axis.text.y=element_text(size=14),axis.title=element_text(size=16,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))
```

<br/>
<br/>

```{r fig4-2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}
ggplot() + geom_bar(aes(y = Count, x = reorder(Team, Count), fill = Type),colour="black",width=.8,alpha=.8, data = pendat,stat="identity")+
  coord_flip()+scale_y_continuous(position = "right")+theme_bw()+scale_fill_brewer(palette="Paired",breaks=pendat$Type,labels=pendat$Type)+
  theme(panel.grid.minor.y=element_blank(),panel.grid.major.y=element_blank())+
  theme(axis.title.y = element_blank())+ylab("Number of 2 min penalties")+
  theme(legend.position="top",legend.title=element_blank(),legend.spacing.x = unit(1, 'cm'),legend.text=element_text(size=13))+
  theme(axis.text.x=element_text(size=18),axis.text.y=element_text(size=14),axis.title=element_text(size=16,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))
```

<br/>
<br/>

```{r fig5-2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 6}
ggplot() + geom_bar(aes(y = Count, x = reorder(Team, Count), fill = Homeaway),colour="black",width=.8,alpha=.8, data = hometab,stat="identity", position="dodge")+
  coord_flip()+scale_y_continuous(position = "right")+theme_bw()+scale_fill_brewer(palette="Paired",breaks=c(1,2),labels=c("Home","Away"))+
  theme(panel.grid.minor.y=element_blank(),panel.grid.major.y=element_blank())+
  theme(legend.position="top",legend.title=element_blank(),legend.spacing.x = unit(0.25, 'cm'),legend.text=element_text(size=12),axis.title.y = element_blank())+ylab("Number of 2 min penalties")+
  theme(axis.text.x=element_text(size=18),axis.text.y=element_text(size=14),axis.title=element_text(size=16,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))
```

<br/>
<br/>

```{r fig6-2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 7}
ggplot() + geom_bar(aes(y = Count/2, x = reorder(Referee,Count), fill = Team),colour="black",width=.8,alpha=.8, data = refcount,stat="identity")+
  coord_flip()+scale_y_continuous(position = "right")+theme_bw()+
  scale_fill_brewer(palette="Paired",breaks=teams,labels=teams_displaynames)+
  theme(panel.grid.minor.y=element_blank(),panel.grid.major.y=element_blank())+
  theme(legend.position="top",legend.title=element_blank(),legend.text=element_text(size=12),axis.title.y = element_blank())+
  ylab("Number of matches as referee")+theme(axis.text.x=element_text(size=18),axis.text.y=element_text(size=14),axis.title=element_text(size=16,face="bold"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))
```

<br/>
<br/>

```{r fig7-2, eval=TRUE,echo=FALSE,fig.width = 10, fig.height = 8}
ggplot() + geom_bar(aes(y = Val, x = reorder(Team, Maxval), fill = Type),colour="black",width=.8,alpha=.8, data = TOItop,stat="identity", position="dodge")+
  coord_flip()+scale_y_continuous(position = "right")+theme_bw()+scale_fill_brewer(palette="Paired",breaks=c("G1","G2","G3","G4"),labels=c("Top 5 players","6-10","11-15","16-20"))+
  theme(panel.grid.minor.y=element_blank(),panel.grid.major.y=element_blank())+
  theme(legend.position="top",legend.title=element_blank(),legend.spacing.x = unit(1, 'cm'),legend.text=element_text(size=12),axis.title.y = element_blank())+ylab("Average time on ice per match (minutes)")+
  theme(axis.text.x=element_text(size=18),axis.text.y=element_text(size=14),axis.title=element_text(size=16,face="bold"))+
  guides(fill = guide_legend(nrow = 1,keywidth=1.2,keyheight=1.2,default.unit="cm"))+
  theme(panel.border = element_blank(),axis.line = element_line(colour = "grey"))
```